Analysis of NLA17 Dissolved Gas Indicator

### 2020-03-04 scripts/dgIndicatorAnalysis.Rmd
I pointed to 2020-02-25.RData and I added a vertical reference line of 1 to the saturation ratio plots.

```{r}
# Read data file
load(paste0(localPath, 
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2020-02-24.RData"))

@@

# look at dissolved concentration indicator
ggplot(pop.eco.sat, aes(estimate, subpopulation)) +
  geom_point() +
  geom_errorbarh(aes(xmax = ucb95pct, xmin = lcb95pct)) +
  facet_wrap(~indicator, scales = "free_x") +
  theme(axis.title = element_blank())

>>>>

```{r}
# Read data file
load(paste0(localPath, 
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2020-02-25.RData"))

@@

# look at dissolved concentration indicator
ggplot(pop.eco.sat, aes(estimate, subpopulation)) +
  geom_point() +
  geom_errorbarh(aes(xmax = ucb95pct, xmin = lcb95pct)) +
  facet_wrap(~indicator, scales = "free_x") +
  theme(axis.title = element_blank()) +
  geom_vline(xintercept = 1)
